---
title: "Introduction to homeR"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to homeR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(homeR)
```

## Introduction

The `homeR` package provides simple utility functions for common tasks. This vignette will show you how to use the main functions in the package.

## Basic Functions

### Hello Function

The `hello()` function provides a simple greeting:

```{r}
hello()
```

You can also provide a custom name:

```{r}
hello("Alice")
```

### Add Numbers Function

The `add_numbers()` function adds two numbers together:

```{r}
add_numbers(2, 3)
```

It works with negative numbers too:

```{r}
add_numbers(10, -5)
```

## Getting Help

To get help on any function, use the `?` operator:

```{r, eval = FALSE}
?hello
?add_numbers
```

## Contributing

This is a template package. Feel free to modify the functions and add new ones according to your needs! 